Reducing iptables configuration complexity using chains

### 2014-04-20 iptables/presentation.tex
remove leading iptables in examples

      \small{iptables -A \textbf{INPUT} -m tcp -p tcp --dport ssh -j ACCEPT}

@@

      \small{iptables -A INPUT \textbf{-m tcp -p tcp --dport ssh -s 10.0.0.0/8} -j ACCEPT}

@@

      \small{iptables -A INPUT -m tcp -p tcp --dport ssh \textbf{-j ACCEPT}}

@@

      iptables -A INPUT -m tcp -p tcp --dport 80 -j ACCEPT\\

>>>>

      \small{-A \textbf{INPUT} -m tcp -p tcp --dport ssh -j ACCEPT}

@@

      \small{-A INPUT \textbf{-m tcp -p tcp --dport ssh -s 10.0.0.0/8} -j ACCEPT}

@@

      \small{-A INPUT -m tcp -p tcp --dport ssh \textbf{-j ACCEPT}}

@@

      \small{-A INPUT -m tcp -p tcp --dport ssh -j ACCEPT\\
      -A INPUT -j DROP}
